Movement for Actors is treated as an interface, with all actors accepting a forward, backwards, upwards, downwards, leftwards, rightwards, and turning rotation. The purpose is to allow the actors a universal application regardless of AI method of locomotion. This also allows an actor to change their form to any other actor without needing to bandage a solution together for each permutation of "from" "to". Anything a player can do, so should any actor of the same type also do.

A secondary reason for this is to decouple direct input from the player in case of interacting using by utilizing a fractional interface than be intercepted and altered. Should a player capture scenario occur where the camera need be free (think the intro sequence to \textit{TESV:Skyrim}), or a scenario where a brainwashed victim's movements all move the player in the same direction (think the Atlas reveal in \textit{Bioshock}), or even a surreal side-scroller section be needed with restricted depth movement. In these, the inputs aren't hardlinked attachments, that must be "handled differently", the inputs filter through a movement interface which can be chained to produce differing behavior.

Movement should also be considered while a player or NPC is engaging with props or other actors. Furniture and interactions will need to be accounted for when dealing with movement inputs, as they can be used as inputs (butter churns, spinning wheels, milking of cows, even scooting over in a bed).

The entire point of this is to remove needed bandages and patches of circumvention to allow behavior not previously definable, but easily implementable. 